Checkpoint 4

### 2020-04-28 Checkpoint 4.Rmd
I plot stuff

>>>>

# Quinn plots stuff
```{r}
a<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
  geom_density(alpha = 0.5)

b<- ggplot(Finaldata, aes(x = Day, y = ChinaVirusInterest, color = factor(State))) + 
    geom_point() + 
    geom_smooth(method = "lm", se = FALSE) + 
    facet_wrap(~ State) + 
    theme(legend.position = "right")

c<- ggplot(Finaldata, aes(x = ChinaVirusInterest, color = factor(StateColor))) + 
    geom_histogram() + 
    facet_wrap(~ Region) +
    theme(legend.position = "right") + 
    scale_colour_manual( values=c("red"= "red3", "blue"= "royalblue", "purple"="darkorchid3"))

d <-  ggplot(Finaldata, aes(y=percent_asian, color = factor(Region))) + 
      geom_boxplot() +
      theme(legend.position = "right")

ggplotly(a)
ggplotly(b)
ggplotly(c)
ggplotly(d)
```
